---
title: "Reproducible science:"
subtitle: "a bioinformatic service perspective"
author: 
  - name: "January Weiner"
    orcid: 0000-0003-1438-7819
    affiliations:
     - ref: cubi
affiliations:
  - id: cubi
    name: Core Unit for Bioinformatics, BIH@Charité
    address: Charitéplatz 1, 
    postal-code: 10117 
    city: Berlin 
    country: Germany
format:
  revealjs:
    transition: fade
    slide-number: true
    smaller: true
    navigation-mode: linear
    self-contained: true
    theme: [default, style.scss]
---

## Three stories

 * Predicting tuberculosis (TB) onset in patients
 * Operating an RNA-Seq pipeline at the CUBI
 * 

## My principles

::: {.incremental}
 * Reproducibility: the analysis should be reproducible with minimal effort
   (always a compromise!); also here: good science practices
 * Accountability: we should be able to trace back every result to its
   underlying data (e.g.: gene set enrichment to differential expression of
   individual genes) with minimal effort; also here: user empowerment
 * Interpretability: we should be able to interpret the results in the
   given biological or medical context; also: collaboration or service?
:::

## Predicting the onset of TB

## Predicting the onset of TB

**Key papers:**

**Weiner 3rd J**, Maertzdorf J, Sutherland JS, Duffy FJ, Thompson E, Suliman S,
McEwen G, Thiel B, Parida SK, Zyla J, Hanekom WA. Metabolite changes in
blood predict the onset of tuberculosis. Nature communications. 2018 Dec
6;9(1):5208.

Suliman S, Thompson EG, Sutherland J, **Weiner 3rd J**, Ota MO, Shankar S,
Penn-Nicholson A, Thiel B, Erasmus M, Maertzdorf J, Duffy FJ. Four-gene
pan-African blood signature predicts progression to tuberculosis. American
journal of respiratory and critical care medicine. 2018 May
1;197(9):1198-208.

Duffy FJ, **Weiner 3rd J**, Hansen S, Tabb DL, Suliman S, Thompson E,
Maertzdorf J, Shankar S, Tromp G, Parida S, Dover D. Immunometabolic
signatures predict risk of progression to active tuberculosis and disease
outcome. Frontiers in immunology. 2019 Mar 22;10:527.

## Slide 1 

To compile, type `quarto render template.qmd`

Make sure you have Quarto 1.2 installed from
[here](https://quarto.org/docs/download/prerelease.html).

::: {.aside}
This aside note can be used to add citations or notes
:::

## Multicolumn slide

:::: {.columns}

::: {.column width="40%" .fragment}
### Left column title

Left column...
:::

::: {.column width="60%" .fragment}
### Right column title

Right column (60%)...

(adding `.fragment` causes the contents to be displayed in steps)
:::

::::



# Part II separator slide {.inverse background-color="$main-accent"}

## Simple numbered and unnumbered lists

:::: {.columns}

::: {.column width="50%"}
 * One
 * Two
:::

::: {.column width="50%"}
 1. One
 2. Two
:::

::::

## Incremental list

::: {.incremental}
 - Item 1
 - Item 2
 - Item 3
:::


## Incremental contents

First part

. . .

Second part


---

This is a slide without a title (use the dashes to separate)

## Transitions {transition="zoom"}

Define them in the YAML header or like here, in the slide title.

Types: none, fade, slide, convex, concave, zoom


## Code 


```{r}
#| echo: true
#| output-location: column-fragment
#| label: fig-sample
#| fig-cap: A dumb plot
plot(1:10)
```

::: {.callout-tip}
Ctrl-click on the image to zoom. And here is a `r pi` for you.
:::

## Code

There are many customization options for the code. For example, you can
highlight (and even animate) certain lines of code:


```{r}
#| code-line-numbers: "|1|2|3|"
#| echo: true
a <- rnorm(10)
b <- rnorm(10) + a
c <- a + b * rnorm(10)
```

You can also specify where precisely should the output of the code go:
below the code (default), on the next slide, on a right-hand column...




## Thank you {.inverse background-color="#70ADC1"}

:::: {.columns}

::: {.column width="40%"}
Acknowledgements

 - N.N.
 - Y.Y.
 
:::

::: {.column width="40%"}
Sources

 - Source 1
 - Source 2
:::

::: {.column width="20%"}

```{r}
#| fig-width: 5
#| fig-height: 5
library(qrcode)
plot(qr_code("https://google.com"))
```



:::


::::
